---
title: "Use of Advanced Tissot Indicatrix package"
output: rmarkdown::html_vignette
author: "Jonas Hurst and Brian Pondi"
date: "04 09 2021"
vignette: >
  %\VignetteIndexEntry{tissot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=6,
  fig.height=4
) 
```

First, we import the advancedtissot package. Then, we import the rnaturalearth package
to retrieve geometries of country boundaries for plots.

```{r setup}
library(advancedtissot)
library(rnaturalearth)
```

Always use this library in combination with package sf, as returned data are
sf-objects.
```{r}
library(sf)
```


## Load data from rnaturalearth
the data for various regions and the world.
```{r}
world <- ne_countries(returnclass = "sf")
norway <- ne_countries(country="norway",returnclass = "sf")
antarctica <- ne_countries(country="antarctica",returnclass = "sf")
kenya <- ne_countries(country="kenya",returnclass = "sf")
```

## Advanced Tissot Indicatrix for the world

The output below is view of the world with distortions in plate caree projections

```{r}
tissot_world <- tissot(world)
plot(tissot_world, areachange = TRUE)
```

The output below is view of the world with distortions in equal area projections
```{r}
plot(tissot_world, crs = "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m no_defs")
```

The output below is view of the world with distortions in Web Mercator projections which has massive area distortions towards the North and South Hemisphere.
```{r}
plot(tissot_world, crs = 3857, areachange = TRUE)
```


## Advanced Tissot Indicatrix for Antarctica

The automatic circle density distribution is not ideal for this region. Therefore we specify it manually through circles_den parameter.

```{r}
tissot_antarctica <- tissot(antarctica, circles_den = c(15, 5))
plot(tissot_antarctica)
```

The output for stereographic projection on Antarctica looks like this:
We can visualize the percentage of area change with the areachange parameter set to TRUE.

```{r}

plot(tissot_antarctica, crs = 3031, areachange = TRUE)
```

## Advanced Tissot Indicatrix for Kenya

For Kenya, the automatically generated circles are a too many on the plot and they can be downsized.

```{r}
tissot_kenya <- tissot(kenya)
plot(tissot_kenya)
```

Downsizing the circles through cricle_size parameter:
Note. Kenya is around the equator hence area distortion is very small.

```{r}
tissot_kenya <- tissot(kenya, circles_den = c(5,9), circle_size = 20000)
plot(tissot_kenya, areachange = TRUE)
```

## Advanced Tissot Indicatrix for Norway

For Norway, the automatic circles look great and you can clearly see the distortion of shape as one moves Northwards.

```{r}
tissot_norway <- tissot(norway)
plot(tissot_norway)
```

## Other functions

General information about tissot object can be obtained through "summary" and "print" functions.

```{r}
summary(tissot_world)
print(tissot_world)
```

We can obtain input geometries and circles as sf objects through "get_geometry" and "get_indicatrix" functions.

```{r}
get_geometry(tissot_world)
get_indicatrix(tissot_world)
```


