---
title: "Use of tissot package"
output: rmarkdown::html_vignette
author: "Jonas Hurst"
date: "01 07 2021"
vignette: >
  %\VignetteIndexEntry{tisot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=6,
  fig.height=4
) 
```

First, we import the tissot package. Then, we import the rnaturalearth package
to retrieve geometries of country boundaries for plots.

```{r setup}
library(tissot)
library(rnaturalearth)
```

Always use this library in combination with package sf, as returned data are
sf-objects.
```{r}
library(sf)
```


## Obtain Tissot's indicatrix circles
You can obtain tissot's indicatrix by calling
```{r}
t_4326 <- tissot()
```


## Plot Tissot's indicatrix
The returned circles are in WGS84 reference system. Therefore, we can use them to visualize distortion in WGS86 plate carrée projection.
For better visualization, countries from rnaturalearth are also added.
```{r}
countries <- st_geometry(ne_countries(returnclass = "sf"))

plot(countries)
plot(t_4326, border="red", add=TRUE)
```

To view distortions of other reference systems, we must transform the indicatrix.
We do this with st_transform() function from the sf package.
In the following, we visualize distortion in Web Mercator Projection.
```{r}
t_3857 <- st_transform(t_4326, 3857)
plot(st_transform(countries, 3857))
plot(t_3857, border="red", add=TRUE)
```

The following visualizes distortion in Eckert-IV projection.
Using PROJ-string to transform, as EPSG-code is not known???
```{r}
t_crs <- st_crs("+proj=eck4 +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m no_defs")
t_54012 <- st_transform(t_4326, t_crs)
plot(st_transform(countries, t_crs))
plot(t_54012, border="red", add=TRUE)
```

The following visualizes distortion in Equal-Earth-Projection
```{r}
t_8857 <- st_transform(t_4326, 8857)
plot(st_transform(countries, 8857))
plot(t_8857, border="red", add=TRUE)
```

